TODO: A Survey of StarCraft AI Techniques

### 2013-01-03 survey.tex
bibliography (CIG 2012)

% POTENTIAL FIELDS:
Potential fields (or influence maps) have been found to be a useful technique for reactive decision making. Some uses of potential fields in RTS games are: avoiding obstacles (navigation), avoiding opponent fire, or staying at maximum shooting distance \cite{Hagelback08,Hagelback09}. Hagelb\"{a}ck and Johansson \cite{HagelbackJ08} presented a multi-agent potential fields based bot able to deal with fog of war in the Tankbattle game. Avery et al. \cite{Avery09} and Smith et al. \cite{SmithCIG10} co-evolved influence map trees for spatial reasoning in RTS games. Danielsiek et al. \cite{Danielsiek_2008} used influence maps to achieve intelligent squad movement to flank the opponent in a RTS game. A drawback for potential field-based techniques is the large number of parameters that has to be tuned in order to achieve the desired behavior. Approaches for automatically learning such parameters have been explored, for example, using reinforcement Learning \cite{Liu_2008}, or self-organizing-maps (SOM) \cite{teamCompositionRTS}. We would like to note that potential fields are a reactive control technique, and as such, they do not perform any form of lookahead. As a consequence, these techniques are prone to make units stuck in local optima.

>>>>

% POTENTIAL FIELDS:
Potential fields (or influence maps) have been found to be a useful technique for reactive decision making. Some uses of potential fields in RTS games are: avoiding obstacles (navigation), avoiding opponent fire, or staying at maximum shooting distance \cite{Hagelback09}. Potential fields have also been combined with A* path-finding to avoid local traps \cite{Hagelback12}. Hagelb\"{a}ck and Johansson \cite{HagelbackJ08} presented a multi-agent potential fields based bot able to deal with fog of war in the Tankbattle game. Avery et al. \cite{Avery09} and Smith et al. \cite{SmithCIG10} co-evolved influence map trees for spatial reasoning in RTS games. Danielsiek et al. \cite{Danielsiek_2008} used influence maps to achieve intelligent squad movement to flank the opponent in a RTS game. A drawback for potential field-based techniques is the large number of parameters that has to be tuned in order to achieve the desired behavior. Approaches for automatically learning such parameters have been explored, for example, using reinforcement Learning \cite{Liu_2008}, or self-organizing-maps (SOM) \cite{teamCompositionRTS}. We would like to note that potential fields are a reactive control technique, and as such, they do not perform any form of lookahead. As a consequence, these techniques are prone to make units stuck in local optima.
